Modelling RNA-based oscillatory circuits

### 2015-09-24 Presentation/MscPresentation.tex
reworking slides
reworked presentation

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

@@

\usepackage{chemfig}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{color}

\title % (optional, use only with long paper titles)
{Modelling RNA Oscillatory Circuits}

@@

\section{Description of RNA Oscillatory system}

\begin{frame}{The RNA Oscillatory System}{}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.
  \begin{center}
  \includegraphics[trim = 0 0 0 30,clip = true,scale = 0.275]{Figures/schematic_initial.png}
  \end{center}

@@

\small
\begin{frame}{Parameters to be estimated in our model}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  \\
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align*}
\end{frame}
\normalsize

@@

\begin{frame}{Parameter Estimation in ODE Model}
  \begin{block}{Goal}
 Estimate unknown parameters in model using time series data.
    \end{block}

@@

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.26, clip = true, trim = 50 0 0 0]{../Figures/13_9_bestPlot}
\end{frame}

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.22, clip = true, trim = 0 0 0 0]{../Figures/13_9_hist}
        \begin{itemize}
    \item Many parameters poorly estimated.
            \end{itemize}
\end{frame}

\begin{frame}{Sensitivity Analysis}
  \includegraphics[scale = 0.22, clip = true, trim = 00 0 0 0]{../Figures/Sensitivty_scaled_other}
          \begin{itemize}
    \item Sensitivity analysis suggests perturbations of several parameters all give similar effects on model output - \alert{hard to resolve}
            \end{itemize}
\end{frame}

\begin{frame}{Model output for all state variables}
  \includegraphics[scale = 0.25, clip = true, trim = 30 0 0 0]{../Figures/model_output}
\end{frame}

@@

\begin{frame}{Simplified Model (1)}
\begin{align*}
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align*}
\begin{itemize}
\item  Model only rate limiting steps - force translation term directly.
\item 3 unknown parameters
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (2)}
  \includegraphics[scale = 0.28, clip = true, trim = 100 0 0 400]{../Figures/13_9_hist_simplified}
  \begin{itemize}
\item  Error values as low as full model
\item Clearer parameter estimation results
\item Two peak structure due to local minima
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (3)}
  \includegraphics[scale = 0.25, clip = true, trim = 60 0 0 00]{../Figures/Likelihood_profile_rough}
    \begin{itemize}
\item  Error landscape, $\Theta = 1000$.
\end{itemize}
\end{frame}

>>>>

\mode<presentation>
{
  \usetheme{default}
  % or ...

@@

\usepackage{epstopdf,chemfig}
\usepackage{xcolor}
\DeclareMathOperator*{\argmin}{arg\,min}
\newenvironment{greyedout}{\color{gray}}{\ignorespacesafterend}

\title % (optional, use only with long paper titles)
{Modelling RNA Circuits}

@@

\section{Description of RNA system}

\begin{frame}{The RNA System}{}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.
  \begin{center}
  \includegraphics[trim = 0 0 0 30,clip = true,scale = 0.275]{Figures/schematic_initial.png}
  \end{center}

@@

\small
\begin{frame}{Full model, with Parameters to be estimated}
\begin{align} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  \\
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\end{frame}
\normalsize

\begin{frame}{Recent Experimental Data}{}
\begin{columns}
\column{.49\textwidth}
\begin{figure}
   \includegraphics[trim = 10 300 270 290,clip = true,scale = 0.55]{Figures/13_9}
\end{figure}
\column{.49\textwidth}
\vspace{-5mm}
\begin{figure}
   \includegraphics[trim = 0 40 0 0 ,page=21 ,clip = true, scale=0.23]{Figures/WCPM_Warwick-talk45-220115.pdf}
\end{figure}
\end{columns}
  \begin{itemize}
    \item Single cell fluoresence time series data (Jaramillo Lab, unpublished).
    \item  Data records $z= z_{0} +\frac{g}{\alert{\Theta}} $
    \end{itemize}
\end{frame}

@@

\begin{frame}{Method for Parameter Estimation in ODE Model}
  \begin{block}{Goal}
 Estimate unknown parameters in model using time series data.
    \end{block}

@@

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.28, clip = true, trim = 80 0 0 0]{Figures/13_9_bestPlot}
\end{frame}

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.25, clip = true, trim = 0 0 0 0]{Figures/13_9_hist}
        \begin{itemize}
    \item Many parameters poorly estimated.
            \end{itemize}
\end{frame}

\begin{frame}{Sensitivity Analysis}
  \includegraphics[scale = 0.2, clip = true, trim = 00 0 0 0]{Figures/Sensitivty_scaled_other}
  \vspace{-2mm}
          \begin{itemize}
    \item Sensitivity analysis suggests perturbations of several parameters all give similar effects on model output - \alert{hard to resolve}
            \end{itemize}
\end{frame}

\begin{frame}{Model output for all state variables}
  \includegraphics[scale = 0.25, clip = true, trim = 30 0 0 0]{Figures/model_output}
\end{frame}

@@

\small
\begin{frame}{Full model again}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align*}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*} 
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align*}
\end{frame}
\normalsize

\small
\begin{frame}{Simplified Model}
\begin{greyedout}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{ds:m}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{dc}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  
\end{align*}
\end{greyedout}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*} 
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}}  
\end{align*}
\end{frame}
\normalsize

\begin{frame}{Simplified Model}
\begin{align}
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\begin{itemize}
\item  Model only rate limiting steps - force translation term directly.
\item 3 unknown parameters
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (1)}
  \includegraphics[scale = 0.28, clip = true, trim = 100 0 0 400]{../Figures/13_9_hist_simplified}
  \begin{itemize}
\item  Error values as low as full model
\item Clearer parameter estimation results
\item Two peak structure due to local minima
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (2)}
  \includegraphics[scale = 0.25, clip = true, trim = 0 0 0 0]{Figures/Likelihood_rough_presentation}
    \begin{itemize}
\item  Error landscape, $\Theta = 5400$.
\end{itemize}
\end{frame}
